Calculating Entropies With Nested Sampling

### 2017-02-27 paper/ms.tex
More sinusoidal writing

A purely sinusoidal signal has the form
\begin{align}
y(t) &= A \sin \left(\frac{2\pi t}{T} + \phi\right)
\end{align}
where $A$ is the amplitude, $T$ is the period, and $\phi$ is the phase.
Throughout this section, I parameterise the period by its logarithm,
$\tau = \log_{10} T$. I assumed the following priors:
\begin{align}
\ln A   &\sim \textnormal{Normal}\left(0, 0.1^2\right)  \\
\tau    &\sim \textnormal{Uniform}(-1, 0)  \\
\phi    &\sim \textnormal{Uniform}(0, 2\pi)
\end{align}
and the following conditional prior for the data:
\begin{align}
d_i | A, T, \phi &\sim \textnormal{Normal}\left(y(t_i), 0.1^2\right).
\end{align}
That is, the data is just the signal $y(t)$ observed at particular times
$\{t_1, ..., t_n\}$, with gaussian noise of standard deviation 0.1.

The multimodality of the posterior here raises an interesting issue. Is
the question we really want answered ``what is the value of $T$
{\bf precisely}?'', to which the mutual information relates?
Most practicing scientists would not feel particularly informed to learn
that the vast majority of possibilities had been ruled out, if the
posterior still consisted of several widely separated modes!
Perhaps, in some applications, a more appropriate question is
``what is the value of $T$ to within $\pm$ 10\%''
{\todo or something like that.}

@@

{\query The multimodality of the posterior in this problem (sometimes) might
affect mixing sufficiently that the NS gets the incorrect answer. Be
careful! And maybe use an example where this is unlikely, or double
check it using brute force.}

@@

\subsection{Uneven observations}
The results for the uneven observing schedule are as follows:
\begin{align}
H'_{\tau}     &= 1.122 \pm 0.028 \\
H'_{\d}       &= 106.8 \pm 1.1   \\
H'_{\tau, \d} &= 97.0 \pm 1.0
I_{\tau, \d} &= 10.9 \pm 0.4
\end{align}
which appears to be higher than under the even observing schedule,
though the uncertainties
are not small enough to be certain of this.

>>>>

A purely sinusoidal signal has the form
\begin{align}
y(t) &= A \sin \left(\frac{2\pi t}{T} + \phi\right)
\end{align}
where $A$ is the amplitude, $T$ is the period, and $\phi$ is the phase.
Throughout this section, I parameterise the period by its logarithm,
$\tau = \log_{10} T$. I assumed the following priors:
\begin{align}
\ln A   &\sim \textnormal{Normal}\left(0, 0.1^2\right)  \\
\tau    &\sim \textnormal{Uniform}(-1, 0)  \\
\phi    &\sim \textnormal{Uniform}(0, 2\pi)
\end{align}
and the following conditional prior for the data:
\begin{align}
d_i | A, T, \phi &\sim \textnormal{Normal}\left(y(t_i), 0.1^2\right).
\end{align}
That is, the data is just the signal $y(t)$ observed at particular times
$\{t_1, ..., t_n\}$, with gaussian noise of standard deviation 0.1.
The amplitude of the sinusoid is very likely to be around 10 times the
noise level, and the period is between 0.1 and 1 times the observation
interval.

@@

@@

\subsection{Uneven observations}
The results for the uneven observing schedule are as follows:
\begin{align}
H'_{\tau}     &= 1.122 \pm 0.028 \\
H'_{\d}       &= 106.8 \pm 1.1   \\
H'_{\tau, \d} &= 97.0 \pm 1.0    \\
I_{\tau, \d} &= 10.9 \pm 0.4
\end{align}
which appears to be higher than under the even observing schedule,
though the uncertainties
are not small enough to be certain of this.

\subsection{Multimodality and precisional questions}

The multimodality of the posterior here raises an interesting issue. Is
the question we really want answered ``what is the value of $T$
{\bf precisely}?'', to which the mutual information relates?
Most practicing scientists would not feel particularly informed to learn
that the vast majority of possibilities had been ruled out, if the
posterior still consisted of several widely separated modes!
Perhaps, in some applications, a more appropriate question is
``what is the value of $T$ to within $\pm$ 10\%''
{\todo or something like that.}
{\query The multimodality of the posterior in this problem (sometimes) might
affect mixing sufficiently that the NS gets the incorrect answer. Be
careful! And maybe use an example where this is unlikely, or double
check it using brute force.}
